A Study of Residual Adapters for Multi-Domain Neural Machine Translation

### 2020-08-15 2020/wmt_20/emnlp2020.tex
remove last comments

The residual adapter architecture extends this model by adding one new computational module for each layer. The $i^{\text{th}}$ residual adapter thus modifies $h^i$ by computing the following transformations:\fyDone{Use align env}
\begin{align*}
  h^{i}_1 &= \mathbf{W}_{db}^{i}h^{i} + b^i_{1} \\
  h^{i}_2 &= \mathbf{ReLU}(h_1^{i})
  \\
%\end{align*}
%\begin{align*}
  h^{i}_3 &= \mathbf{W}_{bd}^{i}h_2^{i} + b^i_{2} \\
  \bar{h}^{i} &= h^{i}_3 + h^i.
\end{align*}
Overall, the  $i^{\text{th}}$ adapter is thus parameterized by matrices $\displaystyle{\mathbf{W}_{db}^{i}\in\mathbb{R}^{d\times b}}$,$\displaystyle{\mathbf{W}_{bd}^{i}\in\mathbb{R}^{b\times d}}$, bias vectors $\displaystyle{b^i_{1} \in \mathbb{R}^{b}}$, $\displaystyle{b^i_{2} \in \mathbb{R}^{d}}$, with $b$ the dimension of the adapter (with $d \gg b$)\fyTodo{Check this}. For the sake of brevity, we will simply denote $h^{i}_3 = \operatorname{ADAP}^{(i)}(h^i)$, and $\theta_{\operatorname{ADAP}^{(i)}}$ the corresponding set of parameters.\fyDone{or is it $h_i$ ?}\fyDone{attention aux matrices $W_i$}

@@

We randomly select in each corpus a development and a test set of 1,000 lines each and keep the rest for training. Development sets help choose the best model according to the average BLEU score \cite{Papineni02bleu}.\footnote{We use truecasing and the \texttt{multibleu} script.}\fyDone{A word about meta-parameter settings} Significance testing is performed using bootstrap resampling \cite{Koehn04statistical}, implemented in compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \cite{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyTodo{Is this part on significance testing still accurate ?}

\subsection{Baseline architectures \label{ssec:baseline}}
\fyTodo{Write this - settings and parameters for Mixed and Full-FT}.
% Our baselines are standard for multi-domain systems.
% \footnote{We however omit domain-specific systems trained only with the corresponding subset of the data, which are always inferior to the mix-domain strategy \cite{Britz17mixing}.}
Using Transformers \cite{Vaswani17attention} implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}, we train the following baselines:
\begin{itemize}
\item a generic model trained on a concatenation of all corpora, denoted \system{Mixed}\fyDone{Or mixed nat ?}
\item a fine-tuned model \cite{Luong15stanford,Freitag16fast}, based on the \system{Mixed} system, further trained on each domain with early stopping when the dev BLEU stops increasing during 3 consecutive epochs.
%  We again contrast two versions: full fine-tuning (\system{FT-Full}), which update all the parameters of the initial generic model \system{Mixed}; and the variants of \cite{Bapna19simple} (\system{FT-Block}).
\end{itemize}

>>>>

The residual adapter architecture extends this model by adding one new computational module for each layer. The $i^{\text{th}}$ residual adapter thus modifies $h^i$ by computing the following transformations:\fyDone{Use align env}
\begin{align*}
  h^{i}_1 &= \mathbf{W}_{db}^{i}h^{i} + b^i_{1} \\
  h^{i}_2 &= \mathbf{ReLU}(h_1^{i})
  \\
%\end{align*}
%\begin{align*}
  h^{i}_3 &= \mathbf{W}_{bd}^{i}h_2^{i} + b^i_{2} \\
  \bar{h}^{i} &= h^{i}_3 + h^i.
\end{align*}
Overall, the  $i^{\text{th}}$ adapter is thus parameterized by matrices $\displaystyle{\mathbf{W}_{db}^{i}\in\mathbb{R}^{d\times b}}$,$\displaystyle{\mathbf{W}_{bd}^{i}\in\mathbb{R}^{b\times d}}$, bias vectors $\displaystyle{b^i_{1} \in \mathbb{R}^{b}}$, $\displaystyle{b^i_{2} \in \mathbb{R}^{d}}$, with $b$ the dimension of the adapter (with $d \gg b$)\fyDone{Check this}. For the sake of brevity, we will simply denote $h^{i}_3 = \operatorname{ADAP}^{(i)}(h^i)$, and $\theta_{\operatorname{ADAP}^{(i)}}$ the corresponding set of parameters.\fyDone{or is it $h_i$ ?}\fyDone{attention aux matrices $W_i$}

@@

We randomly select in each corpus a development and a test set of 1,000 lines each and keep the rest for training. Development sets help choose the best model according to the average BLEU score \cite{Papineni02bleu}.\footnote{We use truecasing and the \texttt{multibleu} script.}\fyDone{A word about meta-parameter settings}
   %    Significance testing is performed using bootstrap resampling \cite{Koehn04statistical}, implemented in compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \cite{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.
\fyFuture{Is this part on significance testing still accurate ?}

\subsection{Baseline architectures \label{ssec:baseline}}
\fyDone{Write this - settings and parameters for Mixed and Full-FT}.
% Our baselines are standard for multi-domain systems.
% \footnote{We however omit domain-specific systems trained only with the corresponding subset of the data, which are always inferior to the mix-domain strategy \cite{Britz17mixing}.}
Using Transformers \cite{Vaswani17attention} implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}, we train the following baselines:
\begin{itemize}
\item a generic model trained on a concatenation of all corpora, denoted \system{Mixed}\fyDone{Or mixed nat ?}
\item a fine-tuned model \cite{Luong15stanford,Freitag16fast}, based on the \system{Mixed} system, further trained on each domain with early stopping when the dev BLEU stops increasing during 3 consecutive epochs.
%  We again contrast two versions: full fine-tuning (\system{FT-Full}), which update all the parameters of the initial generic model \system{Mixed}; and the variants of \cite{Bapna19simple} (\system{FT-Block}).
\end{itemize}
